# HIV Cascade Incidence - Bayesian Results Caomparison
# ====================================================

This Rmarkdown scipt generates the figures and results from the HIV 
cascade incidence analysis. The aim of this analysis is to estimate the
proportion of new infections attributable to GBM living with HIV who are
undiagnosed, diagnosed but not on ART, on ART but with unsuppressed virus,
and those on ART with suppressed virus. 

```{r Initialization}
# Clear workspace
rm(list = ls()) 

# Setup directories after setting working directory to source file 
# directory
basePath <- getwd()

# Various directories
Rcode <- file.path(basePath, "code") 
resultsFolder <- file.path(basePath,"output")

# Load standard libraries, key functions and options
source(file.path(Rcode, "LoadLibrary.R"), echo = TRUE)
source(file.path(Rcode, "DataLibraries.R"), echo = TRUE)

# Source useful functions
source(file.path(Rcode, "BayesFunctions.R"), echo = TRUE)
source(file.path(Rcode, "PlotOptions.R"))
source(file.path(Rcode, "TidyLongitudinal.R"))

```

```{r Load results and plot comparisons}
# Load the previoulsy generated results we want to compare

# Specify the results production times/string for selecting the correct 
# folder
bayesAnalysisTimes <- c("2016-04-14(11-10)", "2016-04-14(13-02)", 
                        "2016-04-14(13-32)")
compareVariable <- "f4"
savePlots <- FALSE

labels <- c("beta" = "Overall beta",
            "beta1" = "Undiagnosed Beta",
            "beta2" = "Diagnosed Beta",
            "beta3" = "Unsuppressed Beta",
            "beta4" = "Suppressed Beta",
            "f1" = "Undiagnosed factor",
            "f2" = "Diagnosed factor",
            "f3" = "Unsuppressed factor",
            "f4" = "Suppressed factor")

# Load Bayesian results
for (time in 1:length(bayesAnalysisTimes)) {
  bayesResultsFolder <- file.path(resultsFolder, 
    paste("Cascade_Bayes_", bayesAnalysisTimes[time], sep = ""))
  load(file.path(bayesResultsFolder, paste(bayesAnalysisTimes[time],
    "_Cascade_Bayes_results.rda", sep = "")))
  
  if (time == 1) {
    # Intilaize result arrays
    priorMatrix <- matrix(0, numBayesSamples, length(bayesAnalysisTimes))
    posteriorMatrix <- priorMatrix
  }
  
  # Create prior and posterior samples
  priorMatrix[, time] <- get(compareVariable)
  posteriorMatrix[, time] <- get(compareVariable)[resampleIndices]
  
}

# Organize results
priors <- as.data.frame(priorMatrix)
colnames(priors) <- c("p1", "p2", "p3")
priors <- gather(priors, "prior", "sample", 1:3)

posteriors <- as.data.frame(posteriorMatrix)
colnames(posteriors) <- c("p1", "p2", "p3")
posteriors <- gather(posteriors, "posterior", "sample", 1:3)

# Plot prior and posterior comparions ------------------------------------

# Labels to specify priors
legLabels <- c("High ART efficacy", "Medium ART efficacy", 
               "Low ART efficacy")

# Prior plot
priorPlot <- ggplot(data = priors, aes(x = sample, group = prior, 
                          colour = factor(prior))) + 
  geom_line(size = 1.2, stat = "density") +  
  scale_colour_brewer(palette = "Set1", name = "Prior",
                      labels = legLabels) + 
  ylab("Density") + 
  xlab(labels[compareVariable]) +
  plotOpts + theme(legend.position = "right")

# Plot prior and posterior comparions 
postPlot <- ggplot(data = posteriors, aes(x = sample, group = posterior, 
                          colour = factor(posterior))) + 
  geom_line(size = 1.2, stat = "density") +  
  scale_colour_brewer(palette = "Set1", name = "Posterior",
                      labels = legLabels) + 
  ylab("Density") + 
  xlab(labels[compareVariable]) +
  plotOpts + theme(legend.position = "right")

if (compareVariable %in% c("f4", "beta4")) {
  # Use logged coordinates
  priorPlot <- priorPlot + scale_x_log10() + 
    xlab(paste(labels[compareVariable], ", log10 scale"))
  postPlot <- postPlot + scale_x_log10() + 
    xlab(paste(labels[compareVariable], ", log10 scale"))
}

if (savePlots) {
  ggsave(file.path(resultsFolder, "Compare_figures", 
    paste("Compare_priors_", compareVariable, ".png", sep = "")), 
    plot = priorPlot, width = 12, height = 10, units = "cm")
  
  ggsave(file.path(resultsFolder, "Compare_figures",
    paste("Compare_posteriors_", compareVariable, ".png", sep = "")), 
    plot = postPlot, width = 12, height = 10, units = "cm")
}

```
