# HIV Cascade Incidence - Bayesian Results Caomparison
# ====================================================

This Rmarkdown scipt generates the figures and results from the HIV cascade
incidence analysis. The aim of this analysis is to estimate the proportion
of new infections attributable to GBM living with HIV who are undiagnosed, 
diagnosed but not on ART, on ART but with unsuppressed virus, and those on 
ART with suppressed virus. 

```{r Initialization}
# Clear workspace
rm(list = ls()) 

# Setup directories after setting working directory to source file 
# directory
basePath <- getwd()

# Various directories
Rcode <- file.path(basePath, "code") 
resultsFolder <- file.path(basePath,"output")

# Load standard libraries, key functions and options
source(file.path(Rcode, "LoadLibrary.R"), echo = TRUE)
source(file.path(Rcode, "DataLibraries.R"), echo = TRUE)

# Source useful functions
source(file.path(Rcode, "BayesFunctions.R"), echo = TRUE)
source(file.path(Rcode, "PlotOptions.R"))
source(file.path(Rcode, "TidyLongitudinal.R"))

```

```{r Load results}
# Load the previoulsy generated results we want to compare

# Specify the results production times/string for selecting the correct 
# folder
bayesAnalysisTimes <- c("2016-04-13(11-30)", "2016-04-13(11-30)", 
                        "2016-04-13(11-30)")

# Load Bayesian results
results <- list()
for (time in 1:length(bayesAnalysisTimes)) {
  bayesResultsFolder <- file.path(resultsFolder, 
    paste("Cascade_Bayes_", bayesAnalysisTime[time], sep = ""))
  load(file.path(bayesResultsFolder, paste(bayesAnalysisTime,
    "_Cascade_Bayes_results.rda", sep = "")))
  
  # Create prior and posterior frames
  priorFrame <- data.frame(beta = beta, 
                           beta1 = beta1,
                           beta2 = beta2,
                           beta3 = beta3,
                           beta4 = beta4,
                           f1 = f1,
                           f2 = f2,
                           f3 = f3,
                           f4 = f4)
  
  posteriorFrame <- data.frame(beta = beta[resampleIndices],
                               beta1 = beta1[resampleIndices],
                               beta2 = beta2[resampleIndices],
                               beta3 = beta3[resampleIndices],
                               beta4 = beta4[resampleIndices],
                               f1 = f1[resampleIndices],
                               f2 = f2[resampleIndices],
                               f3 = f3[resampleIndices],
                               f4 = f4[resampleIndices])

  # Save as list and add to a list
  distributions <- list("priors" = priorFrame, 
                        "posteriors" = posteriorFrame)
  
  results[ii] <- distributions
  
}

# Useful info 
# cascadeBest <- cascadeBestBayes
years <- cascadeBest$year
numyears <- length(years)

```
